---
title: "30daymappinghousingchallenge"
author: "scurry"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    theme: united
    number_sections: FALSE
    toc_float: TRUE
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=FALSE}

setwd("C:/LocalDocuments/GitHub/2024_30daymapchallenge")

knitr::opts_chunk$set(echo = TRUE)

#install.packages("devtools")
devtools::install_github("CityOfPhiladelphia/rphl", force = TRUE)

library(biscale)
library(censusapi)
library(cowplot)
library(dplyr)
library(sf)
library(ggplot2)
library(ggtext)
library(glue)
library(lubridate)
library(mapdeck)
library(cartogram)
library(raster)
library(rphl)
library(tidycensus)
library(tidygeocoder)
library(tidyr)
library(tigris)
library(viridis)

options(tigris_use_cache = TRUE)

```

```{r basemaps, include=FALSE, message=FALSE, warning=FALSE}

options(tigris_use_cache = TRUE)

map_phl_bound <- places(state = "PA", class = "city", cb = TRUE) %>% 
  filter(NAME == "Philadelphia") %>%
  st_transform("EPSG:2272") %>%
  erase_water()

map_states <- states(cb = TRUE) %>%
  st_transform(crs = 5070) 

phlcouncildistricts <- st_read(dsn = "https://services.arcgis.com/fLeGjb7u4uXqeF9q/arcgis/rest/services/Council_Districts_2000/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson")

acs_variable_list.2023 <- load_variables(2023, #year
                                         "acs5", #five year ACS estimates
                                         cache = TRUE)

```


# 30 Day Map(ping Housing) Challenge

Wow, let's give it a go. 

## Day 01 - Points

```{r day01_data, include=FALSE, message=FALSE, warning=FALSE}

query <- paste("SELECT *", "FROM permits")

#this next line only works some of the time - run until it does
d01_data <- rphl::get_carto(query = query, format = "csv", base_url = "https://phl.carto.com/api/v2/sql", stringsAsFactors = FALSE)

#export and read in a copy to not have to wait every time
write.csv(d01_data, "C:/LocalDocuments/GitHub/2024_30daymapchallenge/export/d01_data_save.csv")

```

```{r day01_work, message=FALSE, warning=FALSE}

d01_work <- d01_data %>%
  filter(commercialorresidential == "RESIDENTIAL") %>%
  filter(permittype == "DEMOLITION" | permittype == "RESIDENTIAL BUILDING") 

d01_work <- filter(d01_work, grepl("DEMOLITION|NEW CONSTRUCTION", typeofwork)) 

d01_work$mostrecentinsp <- ymd_hms(d01_work$mostrecentinsp)

d01_work <- d01_work %>%
  filter(mostrecentinsp >= "2024-01-01")

d01_work <- d01_work %>%
  distinct(address, .keep_all = TRUE) 

d01_work <- d01_work %>%
  drop_na(geocode_x, geocode_y)

d01_work <- st_as_sf(d01_work, coords = c("geocode_x", "geocode_y"), crs = 2272)

d01_work$type <- if_else(grepl("DEMOLITION", d01_work$typeofwork), "DEMOLITION", "NEW CONSTRUCTION")

table(d01_work$type)

```

```{r day01_map, message=FALSE, warning=FALSE, fig.width=6, fig.height=6}

demo_color <- "#913047"
newcon_color <- "#516954"
day01_title <- "There have been <span style='color: #913047;'>**296 Demolition**</span> and <span style='color: #516954;'>**1,136 New Construction**</span> \n Residential Permits Issued in Philadlephia in 2024"

ggplot() +
  geom_sf(data = map_phl_bound, color = "white", fill = "gray80") +
  geom_sf(data = d01_work, aes(color = type), size = 0.75) +
  scale_color_manual(values = c(demo_color, newcon_color)) +
  labs(subtitle = day01_title,
       caption = "Data Source: OpenDataPhilly, Licenses & Inspections") +
  theme(plot.subtitle = element_textbox_simple(size = 14, lineheight = 1, halign = 0.5, padding = margin(10, 30, 20, 30)),
        plot.caption = element_textbox_simple(size = 6),
        legend.position = "none",
        panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank())

ggsave(filename = "thumbnails/01_scurry_points.png", width = 6, height = 6, dpi = 300)
```

At the time this data was called, there were more new construction permits pulled than
demolition permits for residential projects, according to the office of Licenses and Inspections. 
This is worth keeping an eye on for the purposes of achieving the Mayors' goal of 
creating more housing to help bring down the cost of housing and ultimately widen the 
tax base.


## Day 02 - Lines

```{r day02_data, include=FALSE, message=FALSE, warning=FALSE}

#data <- url("api.census.gov/data/2023/acs/flows?")
#fromotherstate = "B07204_011"

#download and clean the headers from this website:
#https://www.census.gov/data/tables/time-series/demo/geographic-mobility/state-to-state-migration.html

# d02_data <- read.csv(file = "C:/LocalDocuments/GitHub/2024_30daymapchallenge/data/State_to_State_Migration_Table_2023_T13.csv", header = TRUE)

d02_data <- get_flows(geography = "county",
                       state = c("PA", "DE", "NJ"),
                       year = 2022,
                       output = "long",
                       geometry = TRUE)


```

```{r day02_work, message=FALSE, warning=FALSE}

d02_work <- d02_data %>%
  group_by(FULL2_NAME) %>%
  summarise(totin = sum(MOVEDIN)) %>%
  rename("MOVEDFROM" = "FULL2_NAME") %>%
  mutate(MOVEDTO = "District") %>%
  filter(MOVEDFROM != "Pennsylvania" & MOVEDFROM != "Delaware" & MOVEDFROM != "New Jersey") %>%
  st_drop_geometry()

map_padenj <- map_states %>%
  filter(STUSPS == "PA" | STUSPS == "DE" | STUSPS == "NJ") %>%
  group_by() %>%
  summarise()

map_padenj_ctr <- map_padenj %>%
  st_centroid()

map_padenj_ctr <- extract(map_padenj_ctr, geometry, into = c('Lat', 'Lon'), '\\((.*),(.*)\\)', conv = T)

map_padenj_ctr <- map_padenj_ctr %>%
  mutate(MOVEDTO = "District") %>%
  rename(tolat = "Lat", tolon = "Lon")

map_states_ctr <- map_states %>% 
  st_centroid() %>%
  dplyr::select(NAME) %>%
  rename("MOVEDFROM" = "NAME")

map_states_ctr <- extract(map_states_ctr, geometry, into = c('Lat', 'Lon'), '\\((.*),(.*)\\)', conv = T)

map_states_ctr <- map_states_ctr %>%
  rename(frlat = "Lat", frlon = "Lon")

d02_work_ <- inner_join(d02_work, map_padenj_ctr, by = "MOVEDTO")

d02_work_ <- inner_join(d02_work_, map_states_ctr, by = "MOVEDFROM")

```

```{r day02_map, message=FALSE, warning=FALSE, fig.width=6, fig.height=6}

day02_title <- "New York, Maryland, Florida, and California were the prior homes of over 200,000 new residents who moved to the Third District in 2022"

ggplot() + 
  geom_sf(data = map_states, fill = if_else(map_states$STUSPS == "NY" | map_states$STUSPS == "MD" | map_states$STUSPS == "FL" | map_states$STUSPS == "CA", "lightblue", "gray90"), color = "transparent") +
  geom_sf(data = map_states, fill = "transparent", color = "white", size = 4) +
  geom_sf(data = map_padenj, fill = "darkolivegreen", color = "transparent") +
  geom_curve(data = d02_work_, aes(x = frlat, y = frlon, xend = tolat, yend = tolon), col = "darkslategray4", size = (d02_work_$totin/20000), alpha = 0.5, curvature = 0.2) +
  geom_point(data = d02_work_,
             aes(x = frlat, y = frlon), 
             colour = "darkslategray",
             size = (d02_work_$totin/20000)) +
  geom_point(data = map_padenj_ctr,
             aes(x = tolat, y = tolon), 
             colour = "darkslategray") +
  labs(title = day02_title,
       caption = "Data Source: US Census Bureau, ACS 1-year") +
  theme(plot.title = element_textbox_simple(size = 14, lineheight = 1, halign = 0.5, padding = margin(10, 30, 10, 30)),
        plot.caption = element_textbox_simple(size = 6),
        legend.position = "none",
        panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks = element_blank()) +
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) 

ggsave(filename = "thumbnails/02_scurry_lines.png", width = 6, height = 6, dpi = 300)

```

See a lot of new faces in town lately? Who is moving to the tri-state area and from where are 
they coming? The largest number of newcomers are from New York, but Maryland, California,
and Florida were also top contributors in 2022.

## Day 03 - Polygons

```{r day03_data, include=FALSE, message=FALSE, warning=FALSE}

d03_data <- get_acs(geography = "county",
                    state = c("PA", "DE", "NJ"),
                    variables = c(medsmoc = "B25088_002", medhhinc = "B19019_001"), #median smoc w a mortgage
                    year = 2022,
                    geometry = TRUE,
                    output = "wide"
)

```

```{r day03_work, message=FALSE, warning=FALSE}

d03_work <- d03_data %>%
  mutate(monthly_lw = (medsmocE/0.3)) %>%
  mutate(annual_lw = ((monthly_lw*12))) %>%
  mutate(lw_ratio = (medhhincE/annual_lw)) %>%
  st_transform(crs = 2272)

```

```{r day03_map, message=FALSE, warning=FALSE, fig.width=6, fig.height=6}

d03_map <- cartogram_cont(d03_work, weight = "lw_ratio")

day03_title <- "<span style='color: #3288BD;'>McKean County's</span> <span style='color: #FFFFFF;'>Median Household Income is **1.4 times** more than its Cost of Living & </span> <span style='color: #D53E4F;'>Essex County's</span> <span style='color: #FFFFFF;'>Median Household Income is **.58 times** less than its Cost of Living</span>"

day03_subtitle <- "<span style='color: #FFFFFF;'>Cost of Living is calculated as a living wage where 2022 Median Selected Monthly Ownership Costs of homeowners with a mortgage make up 30% of an annual salary</span>"

day03_caption <- "<span style='color: #FFFFFF;'>Data Source: US Census Bureau, ACS 1-year</span>"

ggplot() +
  geom_sf(data = d03_map, aes(fill = lw_ratio), color = "transparent") +
  geom_sf(data = d03_map, fill = "transparent", color = if_else((d03_map$GEOID == "34013" | d03_map$GEOID == "42083"), "black", "transparent")) +
  scale_fill_distiller(palette = "Spectral", direction = 1) +
  labs(title = day03_title,
       subtitle = day03_subtitle,
       caption = day03_caption) +
  theme(plot.background = element_rect(fill = "black"),
        plot.title = element_textbox_simple(size = 14, lineheight = 1, halign = 0.5, padding = margin(10, 60, 10, 60)),
        plot.subtitle = element_textbox_simple(size = 9, lineheight = 1, halign = 0.5, padding = margin (5, 15, 20, 15)),
        plot.caption = element_textbox_simple(size = 6),
        legend.position = "none",
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

ggsave(filename = "thumbnails/03_scurry_polygons.png", width = 6, height = 6, dpi = 300)

```

There are many ways to measure the difference between household income and cost 
of living expenses. One method includes comparing actual income to a calculated 
salary required to not be cost-burdened by mortgage or rental payments. In McKean County, 
PA, folks have a low cost of living compared to their median income - while the 
cost of living in Essex County, NJ is actually higher than the median income.

## Day 04 - Hexagons

```{r day04_data, include=FALSE, message=FALSE, warning=FALSE}

d04_data <- get_acs(geography = "block group",
                    state = "PA",
                    county = "Philadelphia",
                    variables = c(medyrbuilt = "B25035_001", totpop = "B02001_001", 
                                  totwhitepop = "B02001_002", totblackpop = "B02001_003"), #correlate age to race
                    year = 2022,
                    geometry = TRUE,
                    output = "wide"
)

```

```{r day04_work, message=FALSE, warning=FALSE}

d04_work <- d04_data %>%
  mutate(pcentwhite = totwhitepopE/totpopE,
         pcentnonwhite = 1-(totwhitepopE/totpopE),
         pcentblack = totblackpopE/totpopE) %>%
  mutate(coloroldbg = if_else(pcentnonwhite >= 0.50 & medyrbuiltE <= 1970, TRUE, FALSE)) %>%
  st_centroid()

d04_work <- extract(d04_work, geometry, into = c('Lat', 'Lon'), '\\((.*),(.*)\\)', conv = T)

map_phl_bound_4269 <- map_phl_bound %>%
  st_transform(crs = 4269)

```

```{r day04_map, message=FALSE, warning=FALSE, fig.width=6, fig.height=6}

# ggplot(data = d04_work %>%
#          filter(coloroldbg == TRUE), aes(x = Lat, y = Lon)) + 
#   geom_point() 

#Where are there a high concentration of block groups with predominantly nonwhite hh and median home built before 1970
ggplot() + 
  geom_sf(data = map_phl_bound_4269, color = "white", fill = "gray") +
  geom_hex(data = d04_work %>%
         filter(coloroldbg == TRUE), aes(x = Lat, y = Lon), bins = 40, alpha = 0.85) +
  # ylim(39.9, 40.1) +
  # xlim(-75.3, -75) +
  scale_fill_distiller(palette = "Oranges", direction = 1) +
  annotate("text", x = -75.259, y = 40.01, label = "Haddington", color = "#7B452C", size = 3, fontface = "bold") +
  geom_curve(aes(x = -75.259, xend = -75.247, y = 40.005, yend = 39.973), color = "steelblue", size = 0.8, curvature = 0.25) +
#  annotate("text", x = -75.15, y = 39.9, label = "Cobbs Creek", color = "#7B452C", size = 3, fontface = "bold") +
  annotate("text", x = -75.1, y = 39.95, label = "Point Breeze", color = "#E36D26", size = 3, fontface = "bold") +
  geom_curve(aes(x = -75.1, xend = -75.165, y = 39.943, yend = 39.935), color = "steelblue", size = 0.8, curvature = -0.25) +
  labs(title = "High Risks of Lead in Philadelphia",
       subtitle = "Where are the highest concentrations of block groups with predominantly non-White residents and homes built before 1970?",
       caption = "Data Source: US Census Bureau, ACS 1-year") +
  theme(plot.title = element_textbox_simple(size = 14, lineheight = 1, halign = 0.5, padding = margin(10, 30, 5, 30)),
        plot.subtitle = element_textbox_simple(size = 9, lineheight = 1, halign = 0.5, padding = margin(5, 20, 20, 20)),
        plot.caption = element_textbox_simple(size = 6, lineheight = 1, halign = 1),
        legend.position = "none",
        panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

ggsave(filename = "thumbnails/04_scurry_hexagons.png", width = 6, height = 6, dpi = 300)

# ggplot(data = d04_work, aes(x = medyrbuiltE, y = pcentnonwhite)) + 
#   geom_hex() 

```

Lead pipes have very detrimental effects on the health and wellbeing of residents in 
old cities like Philadelphia. Studies have repeatedly shown that people of color 
and those who live in homes built prior to anti-lead pipe laws in the 1970's are 
especially at risk for the demonstrated ill effects. This map examines every 
Census Tract in Philadelphia County to determine if the area was 
majority non-White AND if the median construction year of homes there was older than 1970. 
The hex map reveals a density of tracts in West and South Philly that mark TRUE for that 
combined factor. 

## Day 05 - Journey

```{r day05_data, include=FALSE, message=FALSE, warning=FALSE}

#https://www.census.gov/data/tables/2020/demo/metro-micro/commuting-flows-2020.html
#remove headers, footers, and convert Workers in Commuting Flow to Numeric column

d05_data <- read.csv(file = "data/d05_source.csv")

map_counties <- counties() %>%
  st_transform(crs = 5070) 

```

```{r day05_work, message=FALSE, warning=FALSE}

d05_work <- d05_data %>%
  filter(Workers.in.Commuting.Flow > MOE) %>%
  drop_na(W.County.FIPS.Code) %>%
  mutate(R.GEOID = (1000 * X...R.State.FIPS.Code) + R.County.FIPS.Code,
         W.GEOID = (1000 * W.State.FIPS.Code) + W.County.FIPS.Code) 

map_counties_ctr <- map_counties %>%
  mutate(R.GEOID = as.numeric(GEOID)) %>% 
  st_centroid() %>%
  dplyr::select(R.GEOID) 

map_counties_ctr <- tidyr::extract(map_counties_ctr, geometry, into = c('Lat', 'Lon'), '\\((.*),(.*)\\)', conv = T)

map_counties_ctr <- map_counties_ctr %>%
  rename(rlat = "Lat", rlon = "Lon")

d05_work <- inner_join(d05_work, map_counties_ctr, by = "R.GEOID", keep = TRUE)

map_counties_ctr <- map_counties_ctr %>%
  rename(wlat = "rlat", wlon = "rlon", W.GEOID = "R.GEOID")

d05_work <- inner_join(d05_work, map_counties_ctr, by = "W.GEOID", keep = FALSE)

d05_work <- d05_work %>%
  mutate(distmeter = pointDistance(d05_work[,c("rlat", "rlon")], d05_work[,c("wlat", "wlon")], lonlat = FALSE)) %>%
  mutate(distmile = distmeter/1609.34)

d05_work <- d05_work %>%
  filter(W.State.Name != "Hawaii" & W.State.Name != "Alaska" & W.State.Name != "Puerto Rico" &
           R.State.Name != "Hawaii" & R.State.Name != "Alaska" & R.State.Name != "Puerto Rico") %>%
  filter(distmile > 0 & distmile < 480)

ggplot() + 
  geom_histogram(data = d05_work %>%
                   filter(distmile > 0 & distmile < 480), aes(x = distmile), fill = "darkolivegreen4", color = "darkolivegreen", bins = 60)

quantile(d05_work$Workers.in.Commuting.Flow)
quantile(d05_work$distmile)

d05_work <- d05_work %>%
  mutate(flowpercentile = case_when(Workers.in.Commuting.Flow <= quantile(d05_work$Workers.in.Commuting.Flow, 0.25) ~ "u25",
                                Workers.in.Commuting.Flow <= quantile(d05_work$Workers.in.Commuting.Flow, 0.50) ~ "u50",
                                Workers.in.Commuting.Flow <= quantile(d05_work$Workers.in.Commuting.Flow, 0.75) ~ "u75",
                                Workers.in.Commuting.Flow > quantile(d05_work$Workers.in.Commuting.Flow, 0.75) ~ "u100")) %>%
  mutate(distpercentile = case_when(distmile <= quantile(d05_work$distmile, 0.25) ~ "u25",
                                    distmile <= quantile(d05_work$distmile, 0.50) ~ "u50",
                                    distmile <= quantile(d05_work$distmile, 0.75) ~ "u75",
                                    distmile > quantile(d05_work$distmile, 0.75) ~ "u100"))

```

```{r day05_map, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}

#low = "lemonchiffon", mid = "darkolivegreen", high = "royalblue4"

#87AFD5
#4F7EAA
#265480
#0B3155

d05_mapa <- ggplot() + 
  geom_segment(data = d05_work %>%
                 filter(flowpercentile == "u25"), aes(x = rlat, y = rlon, xend = wlat, yend = wlon), color = "#E5866C", size = 0.25, alpha = 0.75, curvature = 0.0) +
  geom_segment(data = d05_work %>%
                 filter(flowpercentile == "u50"), aes(x = rlat, y = rlon, xend = wlat, yend = wlon), color = "#8F5443", size = 0.25, alpha = 0.75, curvature = 0.0) +
  geom_segment(data = d05_work %>%
                 filter(flowpercentile == "u75"), aes(x = rlat, y = rlon, xend = wlat, yend = wlon), color = "#435DBA", size = 0.25, alpha = 0.75, curvature = 0.0) +
  geom_segment(data = d05_work %>%
                 filter(flowpercentile == "u100"), aes(x = rlat, y = rlon, xend = wlat, yend = wlon), color = "#2E4080", size = 0.25, alpha = 0.75, curvature = 0.0) +
#  coord_cartesian(xlim = c(-2150000, 2074000), ylim = c(400000, 3500000)) +
  labs(title = " ",
       subtitle = " ", 
       caption = " ") +
  theme(plot.title = element_textbox_simple(size = 14, lineheight = 1, halign = 0.0, padding = margin(0, 0, 0, 0)),
        plot.subtitle = element_textbox_simple(size = 9, lineheight = 1, halign = 0.0, padding = margin(0, 0, 0, 0)),
        plot.caption = element_textbox_simple(size = 6, lineheight = 1, halign = 1),
        legend.position = "none",
        panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

d05_mapb <- ggplot() + 
  geom_segment(data = d05_work %>%
                 filter(distpercentile == "u100"), aes(x = rlat, y = rlon, xend = wlat, yend = wlon), color = "#2E4080", size = 0.25, alpha = 0.75, curvature = 0.0) +
  geom_segment(data = d05_work %>%
                 filter(distpercentile == "u75"), aes(x = rlat, y = rlon, xend = wlat, yend = wlon), color = "#435DBA", size = 0.25, alpha = 0.75, curvature = 0.0) +
  geom_segment(data = d05_work %>%
                 filter(distpercentile == "u50"), aes(x = rlat, y = rlon, xend = wlat, yend = wlon), color = "#8F5443", size = 0.25, alpha = 0.75, curvature = 0.0) + 
  geom_segment(data = d05_work %>%
                 filter(distpercentile == "u25"), aes(x = rlat, y = rlon, xend = wlat, yend = wlon), color = "#E5866C", size = 0.25, alpha = 0.75, curvature = 0.0) +
#  coord_cartesian(xlim = c(-2150000, 2074000), ylim = c(400000, 3500000)) +
  labs(title = " ",
       subtitle = " ", 
       caption = "Data Source: US Census Bureau, ACS 5-year, 2016-2020") +
  theme(plot.title = element_textbox_simple(size = 14, lineheight = 1, halign = 0.0, padding = margin(0, 0, 0, 0)),
        plot.subtitle = element_textbox_simple(size = 9, lineheight = 1, halign = 0.0, padding = margin(0, 0, 0, 0)),
        plot.caption = element_textbox_simple(size = 6, lineheight = 1, halign = 1),
        legend.position = "none",
        panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

d05_map_plotrow <- plot_grid(
  d05_mapa, d05_mapb, 
  nrow = 1, ncol = 2, rel_widths = c(1, 1))

#label_color = c("#2E4080", "#E5866C")

d05_map_title <- ggdraw() + 
  draw_label(
    "Pre-COVID Commute Routes between Residences and Workplaces",
    fontface = "bold",
    size = 16,
    x = 0.5,
    hjust = 0.5
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 10)
  )

d05_map_subtitlea <- ggdraw() +
  draw_label(
    "Heaviest Commute Routes",
    fontface = "bold",
    color = "#2E4080",
    size = 12,
    x = 0.5,
    hjust = 0.5
  )

d05_map_subtitleb <- ggdraw() +
  draw_label(
    "Shortest Commute Routes",
    fontface = "bold",
    color = "#E5866C",
    size = 12,
    x = 0.5,
    hjust = 0.5
  )

d05_map_subtitle <- plot_grid(
  d05_map_subtitlea, d05_map_subtitleb,
  ncol = 2, nrow = 1, rel_widths = c(6, 6)
)

d05_map_top <- plot_grid(
  d05_map_title, d05_map_subtitle,
  ncol = 1, nrow = 2, rel_heights = c(1, 1)
)

plot_grid(
  d05_map_top, d05_map_plotrow,
  ncol = 1, nrow = 2, rel_heights = c(0.1, 1)
)

ggsave(filename = "thumbnails/05_scurry_journey.png", width = 12, height = 6, dpi = 300)

```

Mapping commute routes between residences and workplaces can help inform where 
public transit would be most efficient and see the most use. It's not enough to 
simply look at the heaviest commute routes, but it is also worthwhile to compare 
which routes are longest in order to, again, identify which routes would transport 
the most people over the longest distances. While hubs like Atlanta and DC experience 
heavy amounts of commuters who are coming from short distances, it's interesting 
to see that places like Detroit and Chicago have very heavy amounts of commuters, 
but not from those traveling a short distance.

## Day 12 - TimeAndSpace

```{r day12_data, message=FALSE, warning=FALSE}

d12_data <- read.csv(file = "data/d12_source.csv")

```

```{r day12_work, message=FALSE, warning=FALSE}

d12_work <- d12_data %>%
  filter(yr_pis != 8888 & yr_pis != 9999) %>%
  drop_na(latitude)

d12_work <- d12_work %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4269) %>%
  st_transform(crs = 5070)

d12_work <- d12_work %>%
  mutate(decade = case_when(yr_pis <= 1989 ~ 1980,
                            yr_pis <= 1999 ~ 1990,
                            yr_pis <= 2009 ~ 2000,
                            yr_pis <= 2019 ~ 2010,
                            yr_pis <= 2029 ~ 2020))

map_pa <- map_states %>%
  filter(STUSPS == "PA")

```

```{r day12_map, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}

# Uses grid.arrange to organize independent plots

  
  # Plot 1: Burglaries overlaid on Chicago boundary
d12_mapa <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    geom_sf(data = d12_work %>%
              filter(decade == 1980), color = "violet", size = 0.1) + 
    labs(title = "1980's") +
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
  theme_void() +
  theme(plot.title = element_textbox_simple(size = 14, face = "bold", lineheight = 1, halign = 0.5, padding = margin(0, 0, 0, 0)),
        plot.margin = margin(0, 0, 0, 0),
        legend.position = "none")

d12_mapb <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    geom_sf(data = d12_work %>%
              filter(decade == 1990), color = "mediumpurple1", size = 0.1) + 
    labs(title = "1990's") +
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
    theme_void() +
  theme(plot.title = element_textbox_simple(size = 14, face = "bold", lineheight = 1, halign = 0.5, padding = margin(0, 0, 0, 0)),
        plot.margin = margin(0, 0, 0, 0),
        legend.position = "none")

d12_mapc <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    geom_sf(data = d12_work %>%
              filter(decade == 2000), color = "purple4", size = 0.1) + 
    labs(title = "2000's") +
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
    theme_void() +
  theme(plot.title = element_textbox_simple(size = 14, face = "bold", lineheight = 1, halign = 0.5, padding = margin(0, 0, 0, 0)),
        plot.margin = margin(0, 0, 0, 0),
        legend.position = "none")

d12_mapd <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    geom_sf(data = d12_work %>%
              filter(decade == 2010), color = "slateblue4", size = 0.1) + 
    labs(title = "2010's") +
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
    theme_void() +
  theme(plot.title = element_textbox_simple(size = 14, face = "bold", lineheight = 1, halign = 0.5, padding = margin(0, 0, 0, 0)),
        plot.margin = margin(0, 0, 0, 0),
        legend.position = "none")

d12_mape <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    geom_sf(data = d12_work %>%
              filter(decade == 2020), color = "midnightblue", size = 0.1) + 
    labs(title = "2020's") +
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
    theme_void() +
  theme(plot.title = element_textbox_simple(size = 14, face = "bold", lineheight = 1, halign = 0.5, padding = margin(0, 0, 0, 0)),
        plot.margin = margin(0, 0, 0, 0),
        legend.position = "none")

nbins <- 80
  # Plot 2: Density of burglaries with contours overlaid on Chicago boundary
d12_mapf <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    stat_density2d(data = data.frame(st_coordinates(d12_work %>%
              filter(decade == 1980))),  # Compute 2D kernel density estimate
                   aes(X, Y, fill = ..level.., alpha = ..level..),  # Define aesthetics for density contours
                   size = 0.01, bins = nbins, geom = 'polygon') +  # Set size and number of bins for contours
    scale_fill_viridis() +
    scale_alpha(range = c(0.00, 0.35), guide = FALSE) +  # Set transparency range for contours
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
    theme_void() + 
  theme(plot.margin = margin(0, 0, 0, 0),
        legend.position = "none")  

d12_mapg <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    stat_density2d(data = data.frame(st_coordinates(d12_work %>%
              filter(decade == 1990))),  # Compute 2D kernel density estimate
                   aes(X, Y, fill = ..level.., alpha = ..level..),  # Define aesthetics for density contours
                   size = 0.01, bins = nbins, geom = 'polygon') +  # Set size and number of bins for contours
    scale_fill_viridis() +
    scale_alpha(range = c(0.00, 0.35), guide = FALSE) +  # Set transparency range for contours
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
    theme_void() + 
  theme(plot.margin = margin(0, 0, 0, 0),
        legend.position = "none") 

d12_maph <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    stat_density2d(data = data.frame(st_coordinates(d12_work %>%
              filter(decade == 2000))),  # Compute 2D kernel density estimate
                   aes(X, Y, fill = ..level.., alpha = ..level..),  # Define aesthetics for density contours
                   size = 0.01, bins = nbins, geom = 'polygon') +  # Set size and number of bins for contours
    scale_fill_viridis() +
    scale_alpha(range = c(0.00, 0.35), guide = FALSE) +  # Set transparency range for contours
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
    theme_void() + 
  theme(plot.margin = margin(0, 0, 0, 0),
        legend.position = "none") 

d12_mapi <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    stat_density2d(data = data.frame(st_coordinates(d12_work %>%
              filter(decade == 2010))),  # Compute 2D kernel density estimate
                   aes(X, Y, fill = ..level.., alpha = ..level..),  # Define aesthetics for density contours
                   size = 0.01, bins = nbins, geom = 'polygon') +  # Set size and number of bins for contours
    scale_fill_viridis() +
    scale_alpha(range = c(0.00, 0.35), guide = FALSE) +  # Set transparency range for contours
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
    theme_void() + 
  theme(plot.margin = margin(0, 0, 0, 0),
        legend.position = "none") 

d12_mapj <- ggplot() + 
    geom_sf(data = map_states, fill = "gray85", color = "white") +
    stat_density2d(data = data.frame(st_coordinates(d12_work %>%
              filter(decade == 2020))),  # Compute 2D kernel density estimate
                   aes(X, Y, fill = ..level.., alpha = ..level..),  # Define aesthetics for density contours
                   size = 0.01, bins = nbins, geom = 'polygon') +  # Set size and number of bins for contours
    scale_fill_viridis() +
    scale_alpha(range = c(0.00, 0.35), guide = FALSE) +  # Set transparency range for contours
  xlim(-2150000, 2074000) +
  ylim(400000.00, 3500000) +
    theme_void() + 
  theme(plot.margin = margin(0, 0, 0, 0),
        legend.position = "none") 

d12_map_title <- ggdraw() +
  draw_label(
    "Density of LIHTC Projects by Year Placed in Service",
    fontface = "bold",
    color = "black",
    size = 18,
    x = 0.5,
    hjust = 0.5
  )

d12_map_point <- plot_grid(
  d12_mapa, d12_mapb, d12_mapc, d12_mapd, d12_mape,
  align = "h",
  rel_heights = 1,
  ncol = 5, nrow = 1
  )

d12_map_density <- plot_grid(
  d12_mapf, d12_mapg, d12_maph, d12_mapi, d12_mapj,
  align = "h",
  rel_heights = 1,
  ncol = 5, nrow = 1
  )

d12_map_caption <- ggdraw() +
  draw_label(
    "Data Source: U.S. Department of Housing and Urban Development, LIHTC Property Level Data",
    fontface = "plain",
    color = "black",
    size = 8,
    x = 1,
    hjust = 1
  ) +
  theme(plot.margin = margin(0, 10, 0, 0))

plot_grid(
  d12_map_title, d12_map_point, d12_map_density, d12_map_caption,
  align = "v",
#  rel_heights = c(3, 1, 1, 6),
  ncol = 1, nrow = 4
)

ggsave(filename = "thumbnails/12_scurry_timeandspace.png", width = 12, height = 6, dpi = 300)

```

Mapping where LIHTC projects have been implemented per decade reveals a serious density 
of affordable projects on the Eastern half of the United States and a fairly constant 
presence of projects along the West coast. From decade to decade, the Southern region's 
introduction of LIHTC construction isn't as strong between the 1990's and the 2010's, 
though there has been an increase in recent years.

## Day 13 - A New Tool
```{r d13_data, message=FALSE, warning=FALSE}
#Source: https://www.realtor.com/research/data/

d13_data <- read.csv(file = "data/d13_source.csv")

map_zip <- zctas() %>%
  st_transform(crs = 5070) %>%
  mutate(postal_code = as.numeric(ZCTA5CE20))

map_zip_ctr <- map_zip %>%
  st_centroid()

map_zip_padenj <- st_intersection(map_zip_ctr, map_states)

map_zip_padenj <- map_zip_padenj %>%
  filter(STUSPS == "PA" | STUSPS == "DE" | STUSPS == "NJ") %>%
  mutate(postal_code = as.numeric(ZCTA5CE20)) %>%
  dplyr::select(GEOID, STUSPS, postal_code) %>%
  st_drop_geometry()

map_zip_padenj <- inner_join(map_zip, map_zip_padenj, by = "postal_code")

d13_data_work <- inner_join(map_zip_padenj, d13_data, by = "postal_code") %>%
  st_transform(crs = 2272)

```

```{r d13_work, message=FALSE, warning=FALSE}

d13_data_202202 <- d13_data_work %>%
  filter(month_date_yyyymm == 202202) %>%
  dplyr::select(postal_code, GEOID, STUSPS, month_date_yyyymm, zip_name, 
         median_listing_price, active_listing_count, median_days_on_market, 
         new_listing_count, price_increased_count, price_reduced_count, 
         median_listing_price_per_square_foot, median_square_feet,
         average_listing_price, total_listing_count)

d13_data_202410 <- d13_data_work %>%
  filter(month_date_yyyymm == 202410) %>%
  dplyr::select(postal_code, GEOID, STUSPS, month_date_yyyymm, zip_name, 
         median_listing_price, active_listing_count, median_days_on_market, 
         new_listing_count, price_increased_count, price_reduced_count, 
         median_listing_price_per_square_foot, median_square_feet,
         average_listing_price, total_listing_count)

d13_data_22 <- d13_data_202202 %>%
  dplyr::select(postal_code, GEOID, STUSPS, "22median_listing_price" = median_listing_price,
                "22active_listing_count" = active_listing_count,
                "22total_listing_count" = total_listing_count)

d13_data_24 <- d13_data_202410 %>%
  dplyr::select(postal_code, "24median_listing_price" = median_listing_price,
                "24active_listing_count" = active_listing_count,
                "24total_listing_count" = total_listing_count) %>%
  st_drop_geometry()

d13_data_map <- left_join(d13_data_22, d13_data_24, by = "postal_code")

d13_data_map <- d13_data_map %>%
  mutate(diff_median_listing_price = `24median_listing_price` - `22median_listing_price`,
         diff_active_listing_count = `24active_listing_count` - `22active_listing_count`,
         diff_total_listing_count = `24total_listing_count` - `22total_listing_count`) %>%
  mutate(factor_mlp = case_when(diff_median_listing_price <= 0 ~ as.factor("negative"),
                                diff_median_listing_price > 0 ~ as.factor("positive")),
         factor_alc = case_when(diff_active_listing_count <= 0 ~ as.factor("negative"),
                                diff_active_listing_count > 0 ~ as.factor("positive")),
         factor_tlc = case_when(diff_total_listing_count <= 0 ~ as.factor("negative"),
                                diff_total_listing_count > 0 ~ as.factor("positive")))

d13_data_map <- bi_class(d13_data_map, x = factor_alc, y = factor_mlp, dim = 2)

table(d13_data_map$bi_class)
#!883

```

```{r d13_map, message=FALSE, warning=FALSE}

d13_map <- ggplot() + 
    geom_sf(data = d13_data_map, aes(fill = bi_class), color = "transparent", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = "DkCyan2", dim = 2) +
  labs(
    title = "Did a Housing Inventory Increase Lead to a\n Decrease in Median Listing Price",
    subtitle = "per Tri-State ZIP Code between February 2022 and October 2024?",
    caption = "Data Source: Realtors.com"
  ) +
  theme(plot.title = element_textbox_simple(size = 14, lineheight = 1, halign = 0.5, padding = margin(10, 0, 5, 0)),
        plot.subtitle = element_textbox_simple(size = 9, lineheight = 1, halign = 0.5, padding = margin(5, 0, 20, 0)),
        plot.caption = element_textbox_simple(size = 6, lineheight = 1, halign = 1),
        legend.position = "none",
        panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

d13_legend <- bi_legend(pal = "DkCyan2",
                    dim = 2,
                    xlab = "-/+ Inventory",
                    ylab = "-/+ Price",
                    size = 8)

d13_plot <- ggdraw() +
  draw_plot(d13_map, 0, 0, 1, 1) +
  draw_plot(d13_legend, 0.02, .35, 0.2, 0.2)

d13_plot

ggsave(filename = "thumbnails/13_scurry_anewtool.png", width = 12, height = 6, dpi = 300)

```

Many experts say that housing prices will decrease once inventory increases. According to Realtor.com, the amount of housing inventory for sale in the United States since 2016 was most scarce during February of 2022. Per ZIP code in the tri-state region, which areas have seen housing inventory increases and median listing price decreases? 

During the study period and within the study area, inventory counts and median prices behaved as predicted - either median price increased when inventory decreased or median price decreased when inventory increased - in 35% of recorded cases. More frequently, in areas across the tri-state area where inventory increased, the median price also increased, which occurred in about 58% of recorded cases.

## Day 22 - 2 Colors
```{r d22_data, message=FALSE, warning=FALSE}

d22_data <- st_read(dsn = "https://services.arcgis.com/fLeGjb7u4uXqeF9q/arcgis/rest/services/AffordableHousingProduction/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson")

```

```{r d22_work, message=FALSE, warning=FALSE}



```

```{r d22_map, message=FALSE, warning=FALSE}

new_color <- "#55AFF4"
old_color <- "#142D45"
day22_subtitle <- "and their age from <span style='color: #142D45;'>**old**</span> to <span style='color: #55AFF4;'>**new**</span> in Philadelphia" 

ggplot() + 
  geom_sf(data = map_phl_bound, fill = "gray80", color = "white") +
  geom_sf(data = d22_data %>% filter(status == "Complete"), aes(color = fiscal_year_complete, size = total_units), alpha = 0.25) + 
  labs(title = "Affordable Housing by Total Units",
       subtitle = day22_subtitle,
       caption = "Data Source: OpenDataPhilly") +
  theme(plot.title = element_textbox_simple(size = 14, lineheight = 1, halign = 0.5, padding = margin(10, 0, 5, 0)),
        plot.subtitle = element_textbox_simple(size = 9, lineheight = 1, halign = 0.5, padding = margin(5, 20, 20, 20)),
        plot.caption = element_textbox_simple(size = 6, lineheight = 1, halign = 1),
        legend.position = "none",
        panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

ggsave(filename = "thumbnails/22_scurry_twocolors.png", width = 6, height = 6, dpi = 300)

```

This map depicts the locations of PHA-owned affordable housing facilities throughout 
Philadelphia sorted by age. The newer buildings appear to be located most densely 
in Center City and West Philly, while the older projects are mostly distributed 
in South Philly and also in West Philly. The dearth of affordable housing is 
visible in the northeast region. 

## Day 25 - Heat
```{r d25_data, message=FALSE, warning=FALSE}
#Source: https://opendataphilly.org/datasets/heat-vulnerability-by-census-tract/

d25_data_heat <- st_read(dsn = "data/d25_source.geojson") 

st_crs(d25_data_heat)

d25_data_crime <- read.csv(file = "data/d25_source_crime.csv")

```

```{r d25_work, message=FALSE, warning=FALSE}

table(d25_data_crime$text_general_code)

d25_data_crime_work <- d25_data_crime %>%
  filter(text_general_code == "Aggravated Assault Firearm" | text_general_code == "Robbery Firearm") %>%
  na.omit("lat") %>%
  st_as_sf(coords = c("lng", "lat"), crs = 4326) %>%
  st_transform(crs = st_crs(d25_data_heat))

```

```{r d25_map, message=FALSE, warning=FALSE, fig.width=6, fig.height=6}

ggplot() + 
  geom_sf(data = d25_data_heat, aes(fill = hvi_score), color = "transparent") + 
  scale_fill_steps2(low = "#2C4D00", mid = "#F5F8EF", high = "#AA4639", midpoint = 0, na.value = "white", breaks = seq(-8, 8, 1)) +
  geom_sf(data = d25_data_crime_work, aes(geometry = d25_data_crime_work$geometry), color = "darkred", size = 0.5, alpha = 0.5) +
  geom_sf(data = phlcouncildistricts, fill = "transparent", color = "gray90", size = 12) +
  labs(title = "Packing Heat per Council District",
       subtitle = "Heat Vulnerability Index and Firearm Incidents in 2024",
       caption = "Data Source: OpenDataPhilly") +
  theme(plot.title = element_textbox_simple(size = 14, lineheight = 1, halign = 0.5, padding = margin(10, 30, 5, 30)),
        plot.subtitle = element_textbox_simple(size = 9, lineheight = 1, halign = 0.5, padding = margin(5, 20, 20, 20)),
        plot.caption = element_textbox_simple(size = 6, lineheight = 1, halign = 1),
        legend.position = "none",
        panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

ggsave(filename = "thumbnails/25_scurry_heat.png", width = 6, height = 6, dpi = 300)

```

Several studies show that hotspots for crime are colocated in places where there 
is little tree cover. Synonymously (and in keeping with the day's theme), 
it could also be theorized that crimes that occur with firearms might be colocated 
where heat vulnerability is high. This map aims to begin to test that hypothesis, acknowledging 
that correlation does not equal causation.

## Day 30 - The Final Map
```{r d30_data, message=FALSE, warning=FALSE}

d30_data_vacant <- st_read(dsn = "https://services.arcgis.com/fLeGjb7u4uXqeF9q/arcgis/rest/services/Vacant_Indicators_Land/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson")

d30_data_medhomeval <- get_acs(geography = "tract",
                    state = "PA",
                    county = "Philadelphia",
                    variables = c(medhomevalue = "B25077_001"), 
                    year = 2023,
                    geometry = TRUE,
                    output = "wide"
)

```

```{r d30_work, message=FALSE, warning=FALSE}



```

```{r d30_map, message=FALSE, warning=FALSE}

d30_title <- "<span style='color: #FF0000;'>**Vacant Buildings**</span>" 

ggplot() + 
  geom_sf(data = map_phl_bound, fill = "gray80", color = "white") +
  geom_sf(data = d30_data_medhomeval, aes(fill = medhomevalueE), color = "transparent", alpha = 1) + 
  scale_fill_steps2(low = "#8F9000", high = "#2C4D00", midpoint = 0, na.value = "white", breaks = seq(0, 1000000)) +
  geom_sf(data = d30_data_vacant, fill = "red", color = "transparent", alpha = 0.5) +
  labs(title = d30_title,
       subtitle = "and 2022 Median Home Value",
       caption = "Data Source: OpenDataPhilly, US Census Bureau, ACS 5-year, 2023") +
  theme(plot.title = element_textbox_simple(size = 14, lineheight = 1, halign = 0.5, padding = margin(10, 0, 5, 0)),
        plot.subtitle = element_textbox_simple(size = 9, lineheight = 1, halign = 0.5, padding = margin(5, 20, 20, 20)),
        plot.caption = element_textbox_simple(size = 6, lineheight = 1, halign = 1),
        legend.position = "none",
        panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

ggsave(filename = "thumbnails/30_scurry_thefinalmap.png", width = 6, height = 6, dpi = 300)

```

Residential developers looking for profitable projects might prioritize purchasing property 
in places where there are high "comps" or neighboring homes going for high prices. 
Mapping vacant buildings, as categorized by the City, against 2022 median home value 
shows that Census tracts with high home values have a low density and number of vacant buildings.

# Appendix

## Code That Did Not Work Out
```{r eval=FALSE, include=FALSE}

d04_data <- get_acs(geography = "county",
                    variables = c(avghhsizeoo = "B25010_002", avghhsizero = "B25010_003", 
                                  numbr = "B25041_001"), #median household size owners renters
                    year = 2022,
                    geometry = TRUE,
                    output = "wide"
)

d04_work <- d04_data %>%
  st_centroid()

d04_work <- extract(d04_work, geometry, into = c('Lat', 'Lon'), '\\((.*),(.*)\\)', conv = T)

ggplot(data = d04_work, aes(x = Lat, y = Lon)) + 
  geom_point(aes(color = avghhsizeooE)) +
  xlim(-130, -60) +
  ylim(20, 60)

```

```{r eval=FALSE, include=FALSE}

d04_data <- get_acs(geography = "county",
                    variables = c(medyrbuilt = "B25035_001", totpop = "B02001_001", 
                                  totwhitepop = "B02001_002", totblackpop = "B02001_003"), #correlate age to race
                    year = 2022,
                    geometry = TRUE,
                    output = "wide"
)

d04_work <- d04_data %>%
  mutate(pcentwhite = totwhitepopE/totpopE,
         pcentnonwhite = 1-(totwhitepopE/totpopE),
         pcentblack = totblackpopE/totpopE)

ggplot(data = d04_work, aes(x = medyrbuiltE, y = pcentnonwhite)) + 
  geom_hex() 

```

